### 2016-05-11 text/Chapter03.tex
Add binding to chapter 2, whitespace, tweaks

%!TEX root = ../main.tex

@@

\begin{itemize}
\item The fact that variables are now a vector means that we cannot freely re-order them. This
  guarantees that $\coctx{x\!:\!\tau, y\!:\!\tau}{\alift{\cclrd{\ident{L}}, \cclrd{\ident{D}}}}$
  can not be confused with $\coctx{y\!:\!\tau, x\!:\!\tau}{\alift{\cclrd{\ident{L}}, \cclrd{\ident{D}}}}$.
  We need to define the type system in a way that is similar to sub-structural systems 
  (discussed in Section~\ref{sec:path-logic}) and add explicit rules for manipulating
  the context.

@@

\paragraph{Structural typing rules.}
The structural typing rules are shown in Figure~\ref{fig:applications-struct-live} (b). They mirror
the rules know from sub-structural type systems (Section~\ref{sec:path-logic}). Weakening (\emph{weak})
extends the context with a single unused variable $x$ and adds the $\ident{D}$ annotation to the
vector of coeffects.

>>>>

@@

\begin{itemize}
\item The fact that variables are now a vector means that we cannot freely re-order them. This
  guarantees that $\coctx{x\!:\!\tau, y\!:\!\tau}{\alift{\cclrd{\ident{L}}, \cclrd{\ident{D}}}}$
  can not be confused with $\coctx{y\!:\!\tau, x\!:\!\tau}{\alift{\cclrd{\ident{L}}, \cclrd{\ident{D}}}}$.
  We need to define the type system in a way that is similar to substructural systems
  (discussed in Section~\ref{sec:path-logic}) and add explicit rules for manipulating
  the context.

@@

\paragraph{Structural typing rules.}
The structural typing rules are shown in Figure~\ref{fig:applications-struct-live} (b). They mirror
the rules know from substructural type systems (Section~\ref{sec:path-logic}). Weakening (\emph{weak})
extends the context with a single unused variable $x$ and adds the $\ident{D}$ annotation to the
vector of coeffects.

### 2016-05-11 text/Chapter06.tex
Add binding to chapter 2, whitespace, tweaks

The flat coeffect system captures a number of interesting use-cases (implicit parameters, liveness
and dataflow), but provides relatively imprecise approximation and weak syntactical properties.
Some of those examples can be also seen as per-variable properties. For those, structural coeffect
systems give a more precise information about the context. However, we also look at other applications
that arise from the work on sub-structural logics, a pathway to coeffects discussed in
Section~\ref{sec:path-logic}.

@@

The work in this chapter is more closely related to sub-structural type systems \cite{substruct-attpl-intro}.
Sub-structural systems remove some or all of \emph{weakening}, \emph{contraction} and
\emph{exchange} rules. In contrast, our systems keep all three structural rules, but use them to
manipulate the coeffect annotations in a way that matches the variable manipulations.

@@

The type system for the structural coeffect calculus is similar to sub-structural type systems
in how it handles free variable contexts. The \emph{syntax-driven} rules do not implicitly allow
weakening, exchange or contraction -- this is done by checking the types of sub-expressions
in disjoint parts of the free variable context. Unlike in sub-structural logics, our system
does allow weakening, exchange and contraction, but via explicit \emph{structural} rules that
perform corresponding transformation on the coeffect annotation.

\paragraph{Syntax-driven rules.}
The syntax-driven rules of the type system are shown in Figure~\ref{fig:struct-types} (a).
The variable access rule (\emph{var}) annotates the corresponding variable as being accessed
using $\cunit$. Note that, as in sub-structural systems, the free variable context contains
\emph{only} the accessed variable. Other variables can be introduced using explicit weakening.
Constants (\emph{const}) are type checked in an empty variable context, which is annotated with
an empty vector of coeffect annotations.

@@

\paragraph{Structural rules.}
The rules shown in Figure~\ref{fig:struct-types} (b) are not syntax-directed and
allow different transformation of the free variable context. They correspond to the
transformations known as \emph{weakening}, \emph{exchange} and \emph{contraction}
from sub-structural systems.

@@

In order to choose a unique typing derivation, we follow the example of sub-structural type systems
\cite{substruct-attpl-intro} and introduce a syntax-directed version of the type system (also called
\emph{algorithmic}). This replaces the non-syntax-directed rules for weakening, exchange and
contraction with additional logic in places where contexts are combined. Given a typing derivation
in the syntax-directed type system, we can then produce a matching typing derivation in the original
type system.

>>>>

The flat coeffect system captures a number of interesting use-cases (implicit parameters, liveness
and dataflow), but provides relatively imprecise approximation and weak syntactical properties.
Some of those examples can be also seen as per-variable properties. For those, structural coeffect
systems give a more precise information about the context. However, we also look at other applications
that arise from the work on substructural logics, a pathway to coeffects discussed in
Section~\ref{sec:path-logic}.

@@

The work in this chapter is more closely related to substructural type systems \cite{substruct-attpl-intro}.
Substructural systems remove some or all of \emph{weakening}, \emph{contraction} and
\emph{exchange} rules. In contrast, our systems keep all three structural rules, but use them to
manipulate the coeffect annotations in a way that matches the variable manipulations.

@@

The type system for the structural coeffect calculus is similar to substructural type systems
in how it handles free variable contexts. The \emph{syntax-driven} rules do not implicitly allow
weakening, exchange or contraction -- this is done by checking the types of sub-expressions
in disjoint parts of the free variable context. Unlike in substructural logics, our system
does allow weakening, exchange and contraction, but via explicit \emph{structural} rules that
perform corresponding transformation on the coeffect annotation.

\paragraph{Syntax-driven rules.}
The syntax-driven rules of the type system are shown in Figure~\ref{fig:struct-types} (a).
The variable access rule (\emph{var}) annotates the corresponding variable as being accessed
using $\cunit$. Note that, as in substructural systems, the free variable context contains
\emph{only} the accessed variable. Other variables can be introduced using explicit weakening.
Constants (\emph{const}) are type checked in an empty variable context, which is annotated with
an empty vector of coeffect annotations.

@@

\paragraph{Structural rules.}
The rules shown in Figure~\ref{fig:struct-types} (b) are not syntax-directed and
allow different transformation of the free variable context. They correspond to the
transformations known as \emph{weakening}, \emph{exchange} and \emph{contraction}
from substructural systems.

@@

In order to choose a unique typing derivation, we follow the example of substructural type systems
\cite{substruct-attpl-intro} and introduce a syntax-directed version of the type system (also called
\emph{algorithmic}). This replaces the non-syntax-directed rules for weakening, exchange and
contraction with additional logic in places where contexts are combined. Given a typing derivation
in the syntax-directed type system, we can then produce a matching typing derivation in the original
type system.
